---
title: "Enos 2016: Replication and Extension"
output:
 pdf_document:
  md_extension: +raw_tex
# bibliography: citations.bib
---

```{r setup, include=FALSE}

# Replication of "What the Demolition of Public Housing Teaches Us about the Impact of Racial Threat on Political Behavior"
# Published in American Journal of Political Science (2015)
# Original author: Ryan D. Enos

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stargazer)
library(stringr)
library(extrafont)
library(apsrtable)
```

\begin{flushright}
Gabe Walker

April 10, 2019
\end{flushright}

## Abstract

Abstract goes here.

```{r data, echo=FALSE, message=FALSE, error=FALSE}

# First download the replication file provided on the Harvard Dataverse:
# https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/26612

# Load data.

wtreat <- read.csv("dataverse_files/white.treat.effect.mean.boot.csv")
wtreat.lower <- read.csv("dataverse_files/white.treat.effect.conf.boot.lower.csv")
wtreat.upper <- read.csv("dataverse_files/white.treat.effect.conf.boot.upper.csv")
Nwtreat <- read.csv("dataverse_files/white.treat.N.csv")
btreat <- read.csv("dataverse_files/black.treat.effect.mean.boot.csv")
btreat.lower <- read.csv("dataverse_files/black.treat.effect.conf.boot.lower.csv")
btreat.upper <- read.csv("dataverse_files/black.treat.effect.conf.boot.upper.csv")
Nbtreat <- read.csv("dataverse_files/black.treat.N.csv")

# Letters for marking graphs. One is not used.

use.letters <- c("a", "b", "c", "d", "e", "f", "skip", "g", "h")

# Cycle through each line of data, each of which are groups defined by diferent namepcts.
# Turning into matrices helps below with segment function

for (i in 1:nrow(wtreat)) {
  use.wtreat <- as.matrix(wtreat[i, ])
  use.wlower <- as.matrix(wtreat.lower[i, ])
  use.wupper <- as.matrix(wtreat.upper[i, ])
  use.Nwtreat <- as.matrix(Nwtreat[i, ])

  use.btreat <- as.matrix(btreat[i, ])
  use.blower <- as.matrix(btreat.lower[i, ])
  use.bupper <- as.matrix(btreat.upper[i, ])
  use.Nbtreat <- as.matrix(Nbtreat[i, ])
}
```

```{r graphics, echo=FALSE, message=FALSE, error=FALSE}

# Master parameters for graphics

ylims <- c(-.35, .1)
ylims.2 <- c(-.45, .1)
xlims <- c(.5, 11)
dists <- seq(from = 1000, to = 100, by = -100) ### DELETE THIS LATER
xs <- seq(1:length(dists))
ys <- seq(from = -.35, to = .1, by = .05)
ys.lab <- c("-0.35", "-0.30", "-0.25", "-0.20", "-0.15", "-0.10", "-0.05", "0.00", "0.05", "0.10")
ys.2 <- seq(from = -.45, to = .1, by = .05)
ys.lab.2 <- c("-0.45", "-0.40", "-0.35", "-0.30", "-0.25", "-0.20", "-0.15", "-0.10", "-0.05", "0.00", "0.05", "0.10")

offsets <- .15
text.offsets <- .025
cex.axis <- .9
cex.N <- .7
top.text.adj <- c(1.3, 1.3) ## Offsets on labels to reduce crowding
bottom.text.adj <- c(-.15, -.85)
point.size <- 2
line.offset <- .0175
```

## Figure 1 Treatment Effects

```{r fig1, echo=FALSE, message=FALSE, error=FALSE}

# Set the graphical parameters.

par(las = 1)
par(mar = c(5.1, 4.1, .5, .5))
plot(xs, use.wtreat,
  ylim = ylims,
  xlim = xlims,
  type = "n",
  ylab = "Treatment Effect",
  xlab = "Treated Group Distance from Projects",
  xaxt = "n",
  yaxt = "n.csv"
)
abline(h = 0, lty = 2)

# Draw the error bars first.

segments(
  x0 = xs[1:2] + offsets, x1 = xs[1:2] + offsets, ## only do it for low N blacks because otherwise lines look funny
  y0 = use.btreat[, 1:2], y1 = use.blower[, 1:2]
)
segments(
  x0 = xs[1:2] + offsets, x1 = xs[1:2] + offsets,
  y0 = use.btreat[, 1:2] + line.offset, y1 = use.bupper[, 1:2]
)
## now the others
segments(
  x0 = xs[3:10] + offsets, x1 = xs[3:10] + offsets,
  y0 = use.blower[, 3:10], y1 = use.bupper[, 3:10]
)

segments(
  x0 = xs - offsets, x1 = xs - offsets, ## bottomlines
  y0 = use.wtreat - line.offset, y1 = use.wlower
)
segments(
  x0 = xs - offsets, x1 = xs - offsets, ## toplines
  y0 = use.wtreat, y1 = use.wupper
)

# Lay down the points and add text equal to the sample size.

points(xs - offsets, use.wtreat,
  cex = point.size,
  pch = 21,
  bg = "white",
  col = "black"
)
text(xs - offsets, use.wtreat,
  paste("(", use.Nwtreat, ")", sep = ""),
  cex = cex.N,
  # adj = top.text.adj
  pos = 1
)

points(xs + offsets, use.btreat,
  pch = 16,
  cex = point.size
)
text(xs + offsets, use.btreat,
  paste("(", use.Nbtreat, ")", sep = ""),
  cex = cex.N,
  # adj = bottom.text.adj
  pos = 3
)

# Label the axes.

axis(
  side = 1,
  at = xs,
  label = seq(100, 1000, 100),
  cex.axis = cex.axis
)
axis(
  side = 2,
  at = ys,
  label = ys.lab,
  cex.axis = cex.axis
)
```

***

*Note*: Difference-in-differences results for treatment groups defined by increasing distance from
the demolished projects. Differences are for the mean turnout in 2004 minus the mean turnout
in 2000 for the treatment group minus the same difference for the control group. White circles
represent the mean effect on white voters; black circles represent the mean effect on black voters.
The N in each treatment group is in parentheses next to the mean effect. Vertical lines represent
the 95% confidence intervals generated by bootstrapped standard errors of the difference between
treatment and control.
